Infra-estrutura de Testes para Implementações de Referência do Standard ECMAScript

### 2022-05-11 paper.tex
fix small stuff

\noindent The language starts by asserting that \texttt{obj} is an \texttt{Object} (step 1). Afterwards, getting the value of the property \texttt{length} from \texttt{obj} using the function \texttt{Get}. Converting the previously mentioned value to an Integer that represents the length with the \texttt{ToLength} function, and finally returning said Integer.

>>>>

\noindent The language starts by asserting that \texttt{obj} is an \texttt{Object} (step 1). Afterwards, gets the value of the property \texttt{length} from \texttt{obj} using the function \texttt{Get}. Then, converts the previously mentioned value to an Integer that represents the length with the \texttt{ToLength} function, and finally returns said Integer (step 2).
